\textbf{Response Letter}

### 2018-12-25 doc/aij18/major-revision/letter.tex
Update Dec 25 at 12.18

\textcolor{blue}{We agree with the reviewer's observation, and we believe the misunderstanding stems from us mixing up the words \emph{information} and \emph{observability}. In our claim of FAMA using the minimal amount of information, we should actually say that FAMA uses the \emph{minimal observability} possible, being the extreme case to have only the initial state and final state as observations. In this respect, LOCM is indeed the learning approach that requires the \emph{minimal information} since no state or predicate is needed.}

\textcolor{blue}{We think that LOCM is a learning approach that notably differs from the rest of systems presented in Table XXX and, in this regard, we have highlighted this distinction in section XXXXX.}

>>>>

\textcolor{blue}{We agree with the reviewer's observation, and we believe the misunderstanding stems from us mixing up the words \emph{information} and \emph{observability}. In our claim of \FAMA using the minimal amount of information, we should actually say that \FAMA uses the \emph{minimal observability} possible, being the extreme case to have no actions at all and only the initial state and final state as observations. In this respect, LOCM is indeed the learning approach that requires the \emph{minimal information} since no state or predicate is needed.}

\textcolor{blue}{We think that LOCM is a learning approach that notably differs from the rest of systems presented in Table 2 and, in this regard, we have highlighted this distinction in the explanation of section 2.2. Besides adding a sentence that stresses the ability of LOCM to learning with minimal input knowledge, we devote the last paragraph of section 2.2. to explain the distinctive features of the LOCM family.}
